% Chapter Template

\chapter{Problem Definition and Motivation} % Main chapter title

\label{Chapter:ProblemDefinitionandMotivation}

% Describe the current situation of this problem.
% identifying the obstacles and the possible applications of your research.
% background of the problem (e.g. origins, previous attempts, etc.). 
% State the problem in detail mentioning all relative aspects, variables, relationships,
% stressing on the importance of finding a solution to the problem.

Carbon nanowires have been fabricated with a photoresist by multiple-photon polymerization techniques. However little is known about polymers that can produce conductive carbon nanowires after pyrolysis. In the past years photon polymerization processes have been apllied to the fabrication of nano-structures with the use of a photoresist. \cite{Boer2014} Photon polymerization techniques deliver patterning resolutions with nano-scale tolerances for the production of highly detailed structures. \cite{Hribar2014} Normally Photon polymerization processes can only produce small objects and the resins are often toxic. \cite{Ovsianikov2012}

On the other hand, electrospinning has been acknowledged for as a process with promising results at nano-structure fabrication \cite{Boer2014}, yet there is little research regarding the implementation of electrospinning for the fabrication of carbon nano-wires. Electrospinning has the potential to be a more straightforward process for the design and fabrication of nano-structures, as it can achieve mass scale manufacturing in a continuous, simple and reproducible manner.

Since electrospinning is to be a better alternative for carbon nano-wire synthesis processes, for that purpose, it is required to develop polymer solutions that can be electrospun by near-field electrospinning (NFES) or electromechanic spinning, photopolymerized and pyrolyzed into conducting carbon nanowires. Carbon nano-materials have been subjected to research due to their various potential applications in diverse areas that take advantage of the nano-scale properties. \cite{Siddiqui2019} Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection. \cite{Siddiqui2019} However most application are not currently feasible  due to the lack of a continuous, simple and reproducible fabrication method. With the newly required polymer solution, it would be possible to produce carbon nano-wires in large quantities, and therefore more application will become feasible.






%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------



%-----------------------------------
%	SUBSECTION 1
%-----------------------------------

